### 2020-03-10 CalNotes.tex
update CLT second lemma

\begin{lemma} Let $u^\epl$ be the solution of \eqref{eq:CLT_Poisson} with 

@@

		0 = (V'(z) \otimes V'(x))(A - \alpha - (K - 1)\alpha) - K \sigma \partial^2_{xx}u_0 + \left(K \alpha \cdot V'(x)\right) \partial_x u_0  + \frac1\delta(z-x) \partial_z u_0,

@@

	which, since $A = K\alpha$ and $\Sigma = K\sigma$, implies

@@

@@

	\corr{Idea for the first term:} Let us introduce the notation
	\begin{equation}
	J_1^\epl(T) \defeq \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl\right),
	\end{equation}
	and let us remark that we can rewrite
	\begin{equation} \label{eq:decomposition_first_term}
	\begin{aligned}
	J_1^\epl(T) = \sqrt{T} &\left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\\
		&\quad \times \left(\frac1T \int_0^T \left( \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t)	- V'(Z^\epl_t) \otimes V'(X^\epl_t) \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \dd t	 \right).
	\end{aligned}
	\end{equation}
	Let us denote by $\Phi^\epl$ the solution of \eqref{eq:CLT_Poisson} with right hand side
	\begin{equation}
	\chi^\epl(x, z) = \frac 1 \epl p' \left ( \frac x \epl \right ) V'(z) - V'(z) \otimes V'(x) \mathcal M_\epl^{-1} \mathfrak p_\epl,
	\end{equation}
	and note that $\E^{\rho^\epl}[\chi^\epl(X^\epl,Z^\epl)] = 0$. Then, by Lemma \ref{lem:CLT}, we have
	\begin{equation}
	J_1^\epl(T)= \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \left( -\frac{R^\epl(T)}{T} + \sqrt{2\sigma}\frac{S^\epl(T)}{T} \right),
	\end{equation}
	where $R^\epl(T)$ and $S^\epl(T)$ are defined in \eqref{eq:CLT_PoissonRemainders}. Since \corr{$R^\epl(T)$ is bounded independently of $\epl$ (is it clear?)}, we first get by the ergodic theorem
	\begin{equation}
	\lim_{T \to \infty} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{R^\epl(T)}{\sqrt{T}} = 0, \quad \text{a.s.}
	\end{equation}
	Repeating the same reasoning as for $Q^\epl(T)$ and employing the ergodic theorem and the Slutsky's theorem, we get 
	\begin{equation}
	\lim_{T \to \infty} J_1^\epl(T) = \lim_{T \to \infty} \sqrt{2\sigma} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{S^\epl(T)}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
	\end{equation}
	where the covariance is given by due to \eqref{eq:CLT_Equiv}
	\begin{equation}
	\begin{aligned}
	\Gamma_1^\epl &= 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top} \\
	&= \mathcal M_\epl^{-1}\E^{\rho^\epl}[\Phi^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl) + \chi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top}.
	\end{aligned}
	\end{equation}
	\corr{For the covariance $\Gamma_1^\epl$ we don't know how it behaves in the limit $\epl \to 0$. It would be nice if it was vanishing, but it involves the solution $\Phi^\epl$, which has r.h.s. depending of $\epl$. We noticed that the homogenized problem of
	\begin{equation}
		-\mathcal L_\epl \Phi^\epl = \chi^\epl,
	\end{equation}
	is given by
	\begin{equation}
		-\mathcal L_0 \Phi^0 = 0,
	\end{equation}
	whose zero-mean solution is $\Phi^0 = 0$.}

>>>>

\begin{lemma} \label{lem:CLT_hom}
	Let $u^\epl$ be the solution of \eqref{eq:CLT_Poisson} with 

@@

		0 = (V'(z) \otimes V'(x))(A - \alpha - (K - 1)\alpha) - K \sigma \partial^2_{xx}u_0 + \left(K \alpha \cdot V'(x)\right) \partial_x u_0  + \frac1\delta(z-x) \partial_z u_0.

@@

	Moreover, since $A = K\alpha$ and $\Sigma = K\sigma$, it implies

@@

	\begin{equation}\label{eq:CLT_Poisson_hom}
		- \mathcal L_0 u_0 = 0,
	where $\mathcal L_0$ is the generator of the couple $(X^0,Z^0)^\top$. Finally, the unique solution of \eqref{eq:CLT_Poisson_hom} satisfying
		\E^{\rho^0}[u_0(X,Z)] = 0,
	is given by
		u_0(x,z) = 0.

@@

	\corr{Idea for the first term:} Let us introduce the notation
	\begin{equation}
	J_1^\epl(T) \defeq \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl\right),
	\end{equation}
	and let us remark that we can rewrite
	\begin{equation} \label{eq:decomposition_first_term}
	\begin{aligned}
	J_1^\epl(T) = \sqrt{T} &\left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\\
		&\quad \times \left(\frac1T \int_0^T \left( \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t)	- V'(Z^\epl_t) \otimes V'(X^\epl_t) \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \dd t	 \right).
	\end{aligned}
	\end{equation}
	Let us denote by $u^\epl$ the solution of \eqref{eq:CLT_Poisson} with right hand side
	\begin{equation}
	\chi^\epl(x, z) = \frac 1 \epl p' \left ( \frac x \epl \right ) V'(z) - V'(z) \otimes V'(x) \mathcal M_\epl^{-1} \mathfrak p_\epl,
	\end{equation}
	and note that $\E^{\rho^\epl}[\chi^\epl(X^\epl,Z^\epl)] = 0$. Then, by Lemma \ref{lem:CLT}, we have
	\begin{equation}
	J_1^\epl(T)= \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \left( -\frac{R^\epl(T)}{T} + \sqrt{2\sigma}\frac{S^\epl(T)}{T} \right),
	\end{equation}
	where $R^\epl(T)$ and $S^\epl(T)$ are defined in \eqref{eq:CLT_PoissonRemainders}. Since \corr{$R^\epl(T)$ is bounded independently of $\epl$ (is it clear?)}, we first get by the ergodic theorem
	\begin{equation}
	\lim_{T \to \infty} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{R^\epl(T)}{\sqrt{T}} = 0, \quad \text{a.s.}
	\end{equation}
	Repeating the same reasoning as for $Q^\epl(T)$ and employing the ergodic theorem and the Slutsky's theorem, we get 
	\begin{equation}
	\lim_{T \to \infty} J_1^\epl(T) = \lim_{T \to \infty} \sqrt{2\sigma} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{S^\epl(T)}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
	\end{equation}
	where the covariance is given by due to \eqref{eq:CLT_Equiv}
	\begin{equation}
	\begin{aligned}
	\Gamma_1^\epl &= 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[\partial_x u^\epl(X^\epl, Z^\epl) \otimes \partial_x u^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top} \\
	&= \mathcal M_\epl^{-1}\E^{\rho^\epl}[u^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl) + \chi^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top}.
	\end{aligned}
	\end{equation}
	\corr{For the covariance $\Gamma_1^\epl$ we don't know how it behaves in the limit $\epl \to 0$. It would be nice if it was vanishing since it involves the solution $u^\epl$, which goes to zero (in some sense) due to Lemma \ref{lem:CLT_hom}.}
